Intended Table of Contents Thesis

### 2013-03-05 Chapters/Chapter1/literature_review.tex
Small review per paper

  \item ``Distributed Continuous Action Recognition Using a Hidden Markov Model in Body Sensor Networks''. Single HMM, sensor network cluster movements, HMM constructs continuous actions using postures and actions.*** explain more on this one ***.

>>>>

  \item ``Distributed Continuous Action Recognition Using a Hidden Markov Model in Body Sensor Networks'', cited: 17, 2009. Single HMM, sensor network cluster movements, HMM constructs continuous actions using postures and actions, merges left-to-right HMM for each action to a single. Transcript generation per sensor uses Gaussian Mixed Model, multiple models with $m$ mixtures are trained with Expectation-Maximization (EM), best is chosen.
  \item ``Offline and online activity recognition on mobile devices using accelerometer data'', \cite{duque2012offline}, cited: none, 2012. Compares offline and online methods, cellphone in pocket. Reduces feature extraction (mean and standard deviation (for resources of cellphone). Training is done by database and labeling, classification with K-nearest neighbors, decision trees (C4.5) and decision rules. Online and offline KNN-3 is best, 99\% and 97\%. Six daily activities.
  \item ``Recognizing human activities user-independently on smartphones based on accelerometer data'', \cite{siirtola2012recognizing}, cited: none, 2012. Classifiers K-nearest neighbors and QDA (quadratic discriminant analysis). Online regocnition implemented on phone. five daily activities. Model training by decision tree (active/inactive). Results for QDA, online: 95\%. Activities performed outside.
  \item ``Activity recognition from acceleration data based on discrete consine transform and SVM'', \cite{he2009activity}, cited: 25, 2009. Uses Discrete Cosine Transform (DCT) to get features, PCA to reduce them an multiple SVMs to classify windows. Four daily activities, 97\% precision.
  \item ``Physical Activity Recognition Using a Single Tri-Axis Accelerometer'', \cite{lee2178physical}, cited: 16, 2009. Five daily activities, FFT, fuzzy c means classification, offline. 99\% accuracy. No smartphone, other device.
